---
title: "Hackathon-3-Workout"
author: "Berj Akian"
date: "10/27/2020"
output: html_document
---

# Hackathon 3 - Clustering

Two data files are included in this repo, *engagement-data.csv* represents weekly engagement with the online course for each student. It contains the following variables:

* **id** - student id number
* **modality** - the modality the student was engaging with the platform:  
  * logins - how many times a student logged in that week  
  * video - how many minutes of course videos the student watched that week  
  * forum - how many forum posts the student made that week  
  * game - how many levels of an educational game the student completed that week  
* **measure** - the numerical measure corresponding to the modality (IE - log ins, minutes, posts, levels)  

*student-level.csv* represents student characteristics including assessment results for the students

* **id** - student id number
* **assignment (1-5)** - scores on class assignments (0-100)
* **quiz (1-5)** - score on quizes (0-20)  
* **exam** - score on final exam (0-100)
* **gender** - student self identified gender (a, b, c, d)
* **parent.ed** - highest level of education of parent/guardian
* **race.eth** - student self identified race/ethnicity
* **free-lunch** - whether or not student recieves a free school meal


## Libraries, data loads, and data test 
```{r}
#the magic of tidyverse includes all the following: ggplot2, tibble, tidyr, readr, purrr, dplyr, stringr, forcats
library(tidyverse)

library(data.table)

library(igraph)


#read in files
#student level - Main
#engagement level - activities
main1 <- read.csv("student-level.csv")
act1 <- read.csv("engagement-data.csv")


#copies
spare_act <- act1
spare_main <- main1


#tests to see if there are any goofy records
test1 <- unique(act1$id)
test2 <- unique(act1$modality)
test3 <- unique(act1$week)
test4 <- unique(main1$id)

rm(test1)
rm(test2)
rm(test3)
rm(test4)




```



## Data Restructuring
```{r}


#subtotal the 4 different activities by id and spread them horizontally
act2 <- act1 %>% group_by(id,modality) %>% summarise(sum = sum(measure))
act3 <- spread(act2, modality, sum)



main2 <- main1

#avg the assignment scores and remove the detail
main2$assignmentmean <- main2[,grepl( "assignment" ,names(main2))] %>% rowMeans()
main2 <- select(main2,-assignment1, -assignment2, -assignment3, -assignment4, -assignment5)

#avg the quiz scores and remove the detail
main2$quizmean <- main2[,grepl( "quiz" ,names(main2))] %>% rowMeans()
main2 <- select(main2,-quiz1, -quiz2, -quiz3, -quiz4, -quiz5)


#combine the data.frames
all1 <- full_join(act3, main2, by="id")


#rearrange columns... thank you table.frame!
names(all1)
setcolorder(all1,c("id", "gender", "parent.ed", "race.eth", "free.lunch", "forum", "game", "logins", "video", "assignmentmean", "quizmean", "exam"))
names(all1)



#let's check it out
dim(all1)
summary(all1)

```


## Graphing
```{r}

hist(all1$forum)
hist(all1$game)
hist(all1$logins)
hist(all1$video)

hist(all1$assignmentmean)
hist(all1$quizmean)
hist(all1$exam)


pairs(all1[6:9])
pairs(all1[10:12])
pairs(all1[6:12])

```

## More analysis

```{r}
plot(all1$gender)
```






